\documentclass{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{latexsym}
\usepackage{amsfonts}
\usepackage[normalem]{ulem}
\usepackage{array}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{siunitx}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{listings}
\usepackage{float}
\usepackage[hidelinks]{hyperref}
\usepackage{caption}
\usepackage{logicproof}
\usepackage{longtable}
\usepackage{syntax}
\usepackage[a4paper,left=1in,right=1in,top=1in,bottom=1in]{geometry}

%%% Hyperlink setup
\hypersetup {
	linktoc = none
}

%%% Gramar environment
\setlength{\grammarparsep}{6pt plus 1pt minus 1pt} % increase separation between rules
\setlength{\grammarindent}{12em} % increase separation between LHS/RHS 
\let\syntleft\relax
\let\syntright\relax

%%% Code environment
\usepackage{listings}
\usepackage{xcolor}
\usepackage{mathpartir}
\definecolor{commentsColor}{rgb}{0.497495, 0.497587, 0.497464}
\definecolor{keywordsColor}{rgb}{0.000000, 0.000000, 0.635294}
\definecolor{stringColor}{rgb}{0.558215, 0.000000, 0.135316}

\lstset{
  	basicstyle=\ttfamily\small,                   % the size of the fonts that are used for the code
  	breakatwhitespace=false,                      % sets if automatic breaks should only happen at whitespace
  	breaklines=true,                              % sets automatic line breaking
  	frame=tb,                                     % adds a frame around the code
  	commentstyle=\color{commentsColor}\textit,    % comment style
  	keywordstyle=\color{keywordsColor}\bfseries,  % keyword style
  	stringstyle=\color{stringColor},              % string literal style
  	numbers=left,                                 % where to put the line-numbers; possible values are (none, left, right)
  	numbersep=5pt,                                % how far the line-numbers are from the code
  	numberstyle=\tiny\color{commentsColor},       % the style that is used for the line-numbers
  	showstringspaces=false,                       % underline spaces within strings only
  	tabsize=2,                                    % sets default tabsize to 2 spaces
  	language=c++
}

% Titles
\title{Å Official Documentation}
\author{The official specification for Å}
\date{}
% Custom commands
\newcommand{\newsection}[1]{
	\addcontentsline{toc}{section}{#1}
	\section*{\centering #1}
}
\newcommand{\newsubsection}[1]{
	\addcontentsline{toc}{subsection}{#1}
	\subsection*{#1}
}
\newcommand{\newsubsubsection}[1]{
	\addcontentsline{toc}{subsubsection}{#1}
	\subsubsection*{#1}
}

\begin{document}
\maketitle
\tableofcontents
\thispagestyle{empty}
\newpage
\clearpage
\setcounter{page}{1}
\newsection{Abstract}
This document is the official document for the Å programming language. It shows how a program is parsed from source code into a binary format and then how the binary is executed. Thus this document will also contain the semantics of the language and an explanation for the default implementation of the language.  Besides explaining the semantics and syntax, this document will also explain how the source code is parsed. Additionally, how this parse result is operated on to convert it into a valid piece of Å code.
\\\\
Anything written or discussed within this document is only safely assumed to be applicable for Å version 1.0. Therefore, code and other semantics may be outdated or even too new (or features not implemented yet). This document should, therefore, only act as documentation or as guidance for the previously specified version of Å.
\newpage
\newsection{Using the Virtual Machine}
The virtual machine is first and foremost a command-line tool. It can - on Windows 10 - be run as an executable, wherein it will expect some arguments be given to it. The arguments given to the application will then be used to determine what the application will actually do.
\\\\
The machine is capable of compiling source code into Å byte code. This byte code can then be executed by the machine directly after compilation (Such that it acts as an interpreter of the source code) or be executed later. Besides compiling and executing Å code, the machine is also capable of generating a readable text version of the generated byte code. Letting the user read the result of the compilation. To add to this, the compiler can also unparse the given Abstract Syntax tree that was created during the parsing of the source code. This can help in giving the programmer a bigger insight into the interpretation of the code.
\\\\
Most arguments given to the machine can be executed in sequence (order of arguments is ignored). To which the use of the machine is simplified to simply giving it commands.
\begin{table}[H]
	\centering
	\begin{tabular}{|l|l|c|c|}
	\hline 
	Argument & Description & Available & Version \\ \hline
	\texttt{-ga} & Generate formatted bytecode from compilation & R\textbar D & 1.0 \\ \hline
	\texttt{-lc} & Log the compile time in seconds & R\textbar D & 1.0 \\ \hline
	\texttt{-le} & Log the execute time in seconds & R\textbar D & 1.0 \\ \hline
	\texttt{-silent} & Ignores program output & R\textbar D & 1.0 \\ \hline
	\texttt{-pause} & Will need user input to close & R\textbar D & 1.0 \\ \hline
	\texttt{-trace} & Trace virtual machine operations & D & 1.0 \\ \hline
	\texttt{-test_regressive} & Run regression tests & D & 1.0 \\ \hline
	\texttt{-unparse} & Unparse source after parsing & R\textbar D & 1.0 \\ \hline
	\texttt{-c "input file"} & Compile the input file & R\textbar D & 1.0 \\ \hline
	\texttt{-oae "output file"} & Output operation to specified file & R\textbar D & 1.0 \\ \hline
	\end{tabular}
\end{table}\noindent
Some command arguments (Marked with a 'D') may only work if the VM (The \texttt{C++} code) was compiled with the \texttt{_DEBUG} flag enabled. These operations may severely hinder the performance of the language and the VM and have, therefore, been disabled for public builds. In the case of \texttt{-test_regressive}, it cannot be guaranteed the end user has the files for running the regression tests. This to ensure no error reports of this, or unfortunate crashes, this feature is only available for the developers of Å.
\\\\
As an example, if we wanted to compile and execute a file named "test.aa", with the code:
\begin{lstlisting}
class Program {
	Program() {
		println("Hello World from class");
	}
};

int main() {
	Program p = new Program();
	0;
};

main();
\end{lstlisting}
It could be done with the command arguments:
\begin{center}
\fbox{\texttt{call AAVM.exe -ga -unparse -c "test.aa" -oae "test.aab" -le -lc -pause}}
\end{center}
Which would give a formatted binary file ("test.aab") and an unparsed file alongside the generated binary. Additionally, we'd see the printed message in the console window, as well as the number 0.
\newpage
\newsection{Parsing}
The parsing of Å source code is split into several different stages. The first stage is the lexical analysis. Here each character of the source code is examined and, in the given context, tokenised such that the parse tree has some workable data. The parse tree is constructed by first converting the tokens into parse nodes. This constructs a flattened tree (a simple vector), that, using the syntax rules of the language are expanded. Then the more detailed parsing takes places. Lastly, the whole parse tree is converted into an abstract syntax tree (AST). Afterwards, the parsing result (the AST) is handed off to the compiler.
\\\\
The first parsing error - syntax error - recorded will stop the parsing of the code and immediately report the syntax error to the console. A short explanation of what failed (for example what was expected and what was found) is reported alongside a position (line and column) in code. If possible, a specific syntax error code is also given, hopefully, making it easier to correct or lookup solutions.
\newsubsection{Lexical Analysis}
...
\newsubsection{Parse tree (PT)}
...
\newsubsection{Abstract Syntax Tree (AST)}
...
\newsubsection{Simplifying the AST}
...
\newpage
\newsection{Static Analysis}
...
\newsubsection{Type declarations}
...
\newsubsection{Function Matching}
...
\newsubsection{Building Inheritance Trees}
...
\newsubsection{Control path verification}
...
\newpage
\newsection{Type System}
...
\newsubsection{Static Type Environment}
...
\newsubsection{Dynamic Type Environment}
...
\newsubsection{Typechecking}
...
\newpage
\newsection{Internals of the Virtual Machine}
...
\newsubsection{Executing bytecode}
...
\newsubsection{The operand and call stacks}
...
\newsubsection{The Ref Value Environment}
...
\newsubsection{The Garbage Collector}
\newpage
\newsection{Structure of an Å-binary file}
...
\newpage
\newsection{Compiler}
...
\newsubsection{Compiling the AST}
...
\newsubsection{Verifying Å Bytecode}
...
\newpage
\newsection{Appendix}
The following pages are the appendices of this specification and contain full overview over the grammar, semantics, type rules, compile errors, runtime errors, and instruction list.
\newsubsection{Appendix 1: Complete Overview of Grammar}
\newcommand{\gtext}[1]{<$#1$>}
\newcommand{\glit}[1]{\texttt{#1}}
The following is a BNF grammar - extended with '$^*$' (Kleene Star)\footnote{\url{https://en.wikipedia.org/wiki/Kleene_star}} and '$^+$' (Kleene Plus).
\begin{grammar}
	\gtext{Statement} ::= $Expr$\glit{;}
	\alt $Id$ \glit{=} $Expr$\glit{;} % assignment!	
	
	\gtext{Expr} := \glit{(}$Expr$\glit{)}
	\alt $Expr$ $BinaryOp$ $Expr$
	\alt $PreUnaryOp$ $Expr$
	\alt $Expr$ $PostUnaryOp$
	\alt $IntLit$
	\alt $FloatLit$
	\alt $DoubleLit$
	\alt $BoolLit$
	\alt $NullLit$
	\alt $StringLit$
	\alt $CharLit$
	\alt $Id$
	
	\gtext{Decl} ::= \glit{var} $Id$ $=$ $Expr$\glit{;}
	\alt \glit{const} \glit{var} $Id$ $=$ $Expr$\glit{;}
	\alt $TypeId$ $Id$ $=$ $Expr$\glit{;}
	\alt \glit{class} $Id$ \{ $Decl^*$ \}
	\alt \glit{class} $Id$\glit{()} \{ $Decl^*$ \}
	\alt \glit{class} $Id$\glit{(}$Param$\glit{)} \{ $Decl^*$ \}
	\alt $TypeID$ $Id$\glit{()} \{ $Statement^*$ \}
	\alt \glit{void} $Id$\glit{()} \{ $Statement^*$ \}
	\alt $TypeID$ $Id$\glit{(}$Param$\glit{)} \{ $Statement^*$ \}
	\alt \glit{void} $Id$\glit{(}$Param$\glit{)} \{ $Statement^*$ \}
	
	\gtext{Param} ::= $TypeID$ $Id$ | $Param$\glit{,} $Param$
	
	\gtext{BinaryOp} ::= \glit{+} | \glit{-} | \glit{*} | \glit{/} | \glit{\%} | \glit{\textless} | \glit{\textgreater} | \glit{\textless}= | \glit{\textgreater}= | \glit{==} | \glit{!=} | \glit{+=} | \glit{-=} | \glit{\textbar\textbar} 
	\alt $\&\&$ | \glit{\textbar} | $\&$ | \glit{\textless\textless} | \glit{\textgreater\textgreater}
	
	\gtext{PreUnaryOp} ::= \glit{-} | \glit{!} | \glit{\#}
	
	\gtext{PostUnaryOp} ::= \glit{++} | \glit{--}

	\gtext{Digit} ::= 0 | 1 | 2 | 3 | 4 | 5 | 6 | 7 | 8 | 9

	\gtext{IntLit} ::= $Digit^+$
	
	\gtext{FloatLit} ::= $Digit^+$\glit{.}$Digit^+$\glit{f}
	
	\gtext{DoubleLit} ::= $Digit^+$\glit{.}$Digit^+$
	
\end{grammar}
\newpage
\begin{grammar}
	\gtext{BoolLit} ::= \glit{true} | \glit{false}	
	
	\gtext{NullLit} ::= \glit{null}
	
	\gtext{Letter} ::=  A | B | C | D | E | F | G
       | H | I | J | K | L | M | N
       \alt O | P | Q | R | S | T | U
       | V | W | X | Y | Z | Å 
       \alt a | b | c | d | e | f | g 
       | h | i | j | k | l | m | n 
       \alt o | p | q | r | s | t | u 
       | v | w | x | y | z | å
       
    \gtext{Id} ::= $Letter^+Digit^*Letter^*$ | \glit{_}$Id$
     
    \gtext{Character} ::= $Letter$ | $Digit$ |   | \glit{_} | \glit{+} | \glit{-} | \glit{*} | \glit{/} | \glit{\%} | \glit{\#} | \glit{\textless} | \glit{\textgreater} | \glit{=} | \glit{\textbar} | \glit{\&} | \glit{\$} | \glit{€} | \glit{@} | \glit{£} | \glit{!}
    \alt \glit{?} | \glit{:} | \glit{;} | \glit{,} | \glit{.} | \glit{\^} | \glit{¨} | \glit{\~} | \glit{(} | \glit{)} | \glit{\{} | \glit{\}} | \glit{[} | \glit{]} | \glit{§}
       
	\gtext{StringLit} ::= \glit{\"}$Character^*$\glit{\"}
	
	\gtext{CharLit} ::= \glit{'}$Character$\glit{'}
	
	\gtext{TypeID} ::= \glit{string} | \glit{bool} | \glit{int} | \glit{float} | \glit{char} | \glit{Any} | $Id$
	
\end{grammar}
\newpage
\newsubsection{Appendix 2: Complete Overview of Operational Semantics}
...
\begin{figure}[H]
	\centering
	\begin{mathparpagebreakable}
		\infer[Rule]
		{top}
		{bottom}
	\end{mathparpagebreakable}
\end{figure}
\newpage
\newsubsection{Appendix 3: Complete Overview of Typing Rules}
...
\newpage
\newsubsection{Appendix 4: Complete Overview of Compile Errors}
\newpage
\newsubsection{Appendix 5: Complete Overview of Instruction List}
A complete and fully up to date list can be found \underline{\href{https://github.com/JustCodiex/AA/blob/master/AAByteCode.h}{here}}.
\begin{longtable}{|l|c|c|c|c|c|c|c|}
		\hline
		\# & Opcode & Arguments & Stack before & Stack after & Description & Notes & Version \\ \hline
		0 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		1 & \texttt{PUSHC} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		2 & \texttt{PUSHN} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		3 & \texttt{PUSHV} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		4 & \texttt{PUSHWS} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		5 & \texttt{ADD} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		6 & \texttt{SUB} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		7 & \texttt{MUL} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		8 & \texttt{DIV} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		9 & \texttt{MOD} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		10 & \texttt{NNEG} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		11 & \texttt{CONCAT} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		12 & \texttt{LEN} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		13 & \texttt{INC} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		14 & \texttt{DEC} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		15 & \texttt{SETVAR} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		16 & \texttt{GETVAR} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		17 & \texttt{SETFIELD} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		18 & \texttt{GETFIELD} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		19 & \texttt{GETELEM} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		20 & \texttt{SETELEM} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		21 & \texttt{JMP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		22 & \texttt{JMPF} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		23 & \texttt{JMPT} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		24 & \texttt{LJMP} & & TBD & TBD & No operation & Not used & \textsf{V1.0} \\ \hline
		25 & \texttt{CALL} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		26 & \texttt{VCALL} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		27 & \texttt{XCALL} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		28 & \texttt{RET} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		29 & \texttt{CMPE} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		30 & \texttt{CMPNE} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		31 & \texttt{LE} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		32 & \texttt{GE} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		33 & \texttt{GEQ} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		34 & \texttt{LEQ} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		35 & \texttt{LNEG} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		36 & \texttt{LAND} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		37 & \texttt{LOR} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		38 & \texttt{BAND} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		39 & \texttt{BOR} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		40 & \texttt{TUPLECMP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		41 & \texttt{TUPLENEW} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		42 & \texttt{TUPLEGET} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		43 & \texttt{ALLOC} & & TBD & TBD & No operation & Not used & \textsf{V1.0} \\ \hline
		44 & \texttt{ALLOCARRAY} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		45 & \texttt{CTOR} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		46 & \texttt{TRY} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		47 & \texttt{THROW} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		48 & \texttt{BRK} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		49 & \texttt{POP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		50 & \texttt{CASTI2F} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		51 & \texttt{CASTF2I} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		52 & \texttt{CASTF2I} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		53 & \texttt{CASTS2F} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		54 & \texttt{CASTF2S} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		55 & \texttt{CASTL2F} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		56 & \texttt{CASTL2I} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		57 & \texttt{CASTL2S} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		58 & \texttt{CASTF2L} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		59 & \texttt{CASTI2D} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		60 & \texttt{CASTS2D} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		61 & \texttt{CASTF2D} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		62 & \texttt{CASTL2D} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		63 & \texttt{CASTD2I} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		64 & \texttt{CASTD2S} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		65 & \texttt{CASTD2F} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		66 & \texttt{CASTD2L} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		67 & \texttt{WRAP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		68 & \texttt{UNWRAP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		69 & \texttt{BCKM} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		70 & \texttt{BDOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		71 & \texttt{EXTTAG} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%72 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%73 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%74 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%75 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%76 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%77 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%78 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%79 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%80 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%81 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%82 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%83 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%84 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%85 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%86 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%87 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%88 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%89 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%90 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%91 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%92 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%93 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%94 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%95 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%96 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%97 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%98 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
		%99 & \texttt{NOP} & & TBD & TBD & No operation & & \textsf{V1.0} \\ \hline
	\end{longtable}
\end{document}